Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-19 paper/paper.tex
pass on RQ2

This section reports results of test transplantation. More
specifically, we analyzed the failures observed when running a test
suite original from a given engine in another engine. Intuitively, we
want to assess how effective is the idea of cross-fertilization of
knowledge among \js\ developers.

%\vspace{0.5ex}
\subsubsection{Methodology}
\label{sec:methodology}
In this experiment, a developer with experience in \js\ analyzed each
test file that reveals failure in a given engine and classified that
file as potentially fault-revealing or not. The co-authors supervised
the classification process to validate correctness. For the cases the
developer classified the failures as potentially fault-revealing, one
of the co-authors carefully inspected the case and reported the bug,
if confirmed, or re-classified the failure as a false alarm.

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. As explained in
Section~\ref{sec:seeds}, we used in this experiment the
\totalTestFilesForTestTransplantation{} tests included in the circle
from Table~\ref{tab:test-suites}. Running those tests we observed a
total of 812 failures manifested across 543 distinct files (8.9\% of
total). Table~\ref{tab:cross-testing} shows that, considering the
engines analyzed, \smonkey\ was the engine that failed the least
whereas \chakra\ was the engine that failed the most. The
\smonkey\ test suite also revealed more failures than any other,
perhaps as expected, considering that it is the suite with more tests
(see Table~\ref{tab:test-suites}).

@@

\sloppy
The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture looking for error types like \CodeIn{ReferenceError}
and \CodeIn{TypeError}. For example, we found cases where the test (or
its harness) capture the corresponding exception, making the test to
fail in an assertion instead.  \textbf{Other.} This category includes
other sources. For example, it includes the cases where the test was
valid for some previous version of the spec but is no longer valid for
the current spec.

\begin{wraptable}[12]{r}{0.23\textwidth}  
  \small
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
    of False (FP) and True Positives (TP).}
  \setlength{\tabcolsep}{3pt}      
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{FP} & Undefined Behavior & 252 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 119 \\
    & Other & 135 \\
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{wraptable}
Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' was the most predominant source. Considering true
positives, we found a reasonable number of duplicate reports, but not
enough high to justify attempting to automate the detection of
duplicates.  Table~\ref{tab:test-transplantation-bugs} lists all bugs
we found with test transplantation. The first column shows the
identifier we assigned to the bug\Comment{, column ``Date'' shows the
  date the bug was reported in the format ``m/dd'',}, column
``Engine'' shows the affected engine, column ``Status'' shows the
status of the bug report at the time of the writing. The status string
appears in bold face for status ``Confirmed'' or higher, \ie{},
``Assigned'' and ``Fixed''.  Column ``Severity'' shows the
severity of confirmed bugs, and, finally, column ``Suite''
shows the name of the engine that originated the test.

@@

Considering severity levels, it is worth noting that
\jsc{}~\cite{jsc-severity} and \smonkey{}~\cite{mozilla-severity} uses
five levels, whereas \chakra{}~\cite{chakra-severity} and
\veight{}~\cite{v8-severity} use only three. As usual, the smallest
the severity value the highest the severity of the bug. We use a dash
(``-'') in place of the severity level for the cases where the bug
report is pending confirmation. Of the \noBugsTransplantation{} bugs
we reported in this experiment, \noBugsTransplantationConfirmed\ were
promoted from the status ``New'' to ``Confirmed''. Of these, 16 are
severity-2 bugs.  Although we did not find any critical bugs, most of
the bugs are seemingly important as per the categorization given by
engineers. Analyzing the issue tracker of \chakra, we found that
severity-1 bugs are indeed rare. Considering the bug reports confirmed
by developers, \chakra{} was the engine with the highest number--12
(with 3 bugs fixed). Considering the remaining engines, \veight{}
developers confirmed the three bugs we reported, fixing
one. Curiously, Google engineers confirmed the report we issued in a
few hours. Overall, we found that development teams of other engines,
specially \jsc\, took much longer to analyze bug reports as can be
observed in the \jsc\ stacked bar from
Figure~\ref{fig:stacked-engine}. Curiously, however, the bugs that the
\jsc{} team confirms are quickly fixed.

>>>>

This section reports results of test transplantation. More
specifically, we analyzed the failures observed when running a test
suite original from a given engine in another engine. Intuitively, we
want to assess how effective is the idea of cross-fertilization of
testing knowledge among \js\ developers.

%\vspace{0.5ex}
\subsubsection{Methodology}
\label{sec:methodology}
In this experiment, a developer with experience in \js\ analyzed each
test failure, affecting a particular engine, and classified that
failure as potentially fault-revealing or not. The authors supervised
the classification process to validate correctness. For the
potentially fault-revealing cases, one of the authors carefully
inspected the scenario and, if agreed on the classification, reported
the bug on the issue tracker of the affected engine.

%If not, re-classified the failure as a false alarm.

@@

\Fix{Igor, please check these numbers! The status of most reports should
  have changed.}

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. As explained in
Section~\ref{sec:seeds}, we used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from Table~\ref{tab:test-suites} in this experiment. Running those
tests we observed a total of 812 failures manifested across 543
distinct files (8.9\% of total). Table~\ref{tab:cross-testing} shows
that \smonkey\ was the engine that failed the least whereas
\chakra\ was the engine that failed the most. The \smonkey\ test suite
also revealed more failures than any other, perhaps as expected,
considering that it is the suite with more tests (see
Table~\ref{tab:test-suites}).

@@

\sloppy The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} did not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture that by looking for error types like
\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example, we found
cases where the test (or its harness) fails in an assertion because of
an undefined property.}
\textbf{Other.} This category includes other sources. For example, it
includes the cases where the test was valid for some previous version
of the spec but is no longer valid for the current spec.

\begin{wraptable}[12]{r}{0.23\textwidth}
  \vspace{-3ex}
  \small
  \centering
  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
    of False (FP) and True Positives (TP).}
  \setlength{\tabcolsep}{3pt}      
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{ccr}
    \toprule
    & source &  \#\\
    \midrule
    \multirow{5}{*}{FP} & Undefined Behavior & 252 \\
    & Timeout/OME & 15 \\
    & Not Implemented & 22 \\
    & Non-Standard Element & 119 \\
    & Other & 135 \\
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 10 \\
    & Bug & 24 \\
    \bottomrule
  \end{tabular}
\end{wraptable}
Table~\ref{fig:piecharts-transplantation} shows the distribution of
False Positives (FPs) and True Positives (TPs). Considering false
positives, ``Undefined Behavior'' was the most predominant
source. Considering true positives, we found a reasonable number of
duplicate reports, but not high enough to justify attempting to
automate the detection of duplicates.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Severity'' shows the severity of confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.  (We omitted the URLs of the issues to protect anonymity.)
Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
and \smonkey{}~\cite{mozilla-severity} developers use five levels,
whereas \chakra{}~\cite{chakra-severity} and
\veight{}~\cite{v8-severity} developers use only three. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') in place of the severity level for the cases where
the bug report is pending confirmation. Of the
\noBugsTransplantation{} bugs we reported in this experiment,
\noBugsTransplantationConfirmed\ were promoted from the status ``New''
to ``Confirmed''. Of these, 16 are severity-2 bugs.  Although we did
not find any critical bugs, most of the bugs are seemingly important
as per the categorization given by engineers. Analyzing the issue
tracker of \chakra, we found that severity-1 bugs are indeed
rare. Considering the number of bug reports confirmed by developers,
\chakra{} was the engine with the highest number--12 (with 3 bugs
fixed). Considering the remaining engines, \veight{} developers
confirmed the three bugs we reported, fixing one. Curiously, Google
engineers confirmed the issued bug reports in a few hours. Overall, we
found that development teams of other engines, specially \jsc\, took
much longer to analyze bug reports as can be observed in the
\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
However, the bugs the \jsc{} team confirmed were quickly fixed.
